\Large\textbf{Version}
\normalsize

This is the fifth major draft of this document since 2009.

\begin{enumerate}
\item \textbf{HTML Version}   - http://dev.stephendiehl.com/hask/index.html
\item \textbf{PDF Version}    - http://dev.stephendiehl.com/hask/tutorial.pdf
\item \textbf{EPUB Version}   - http://dev.stephendiehl.com/hask/tutorial.epub
\item \textbf{Kindle Version} - http://dev.stephendiehl.com/hask/tutorial.mobi
\end{enumerate}

Pull requests are always accepted for changes and additional content. This is a
living document.  The only way this document will stay up to date and accurate
through the kindness of readers like you and community patches and pull requests
on Github. https://github.com/sdiehl/wiwinwlh

\textbf{Publish Date}: \today \\
\textbf{Git Commit:} \texttt{\input{.git/ORIG_HEAD}}

\par\noindent\rule{\textwidth}{0.4pt}

\Large\textbf{Author}
\normalsize

This text is authored by Stephen Diehl.

\begin{enumerate}
\item Web: www.stephendiehl.com
\item Twitter: https://twitter.com/smdiehl
\item Github: https://github.com/sdiehl
\end{enumerate}

Copyright \textcopyright \ 2009-2020 Stephen Diehl

This code included in the text is dedicated to the public domain.  You can copy,
modify, distribute and perform the work, even for commercial purposes, all
without asking permission.

You may distribute this text in its full form freely, but may not reauthor or
sublicense this work. Any reproductions of major portions of the text must
include attribution.

The software is provided “as is”, without warranty of any kind, express or
implied, including But not limited to the warranties of merchantability, fitness
for a particular purpose and noninfringement. In no event shall the authors or
copyright holders be liable for any Claim, damages or other liability, whether
in an action of contract, tort or otherwise, Arising from, out of or in
connection with the software or the use or other dealings in the software.
